GEE models

### 2017-07-11 doc/manuscript.Rmd
clarified esm fig refs

A number of associations were seen in the unadjusted GEE models 
(see `r cite_sf('gee')`), particularly for NEFA modeled as a concentration.
While full model adjustment (`r cite_f('gee')`) attenuated most of these
associations, total NEFA, 16:0, 18:1n-9, and 18:2n-6 (all as nmol/mL)
continued to show negative associations with IGI/IR and ISSI-2. Sensitivity
analyses revealed that adjustment for WC was responsible for attenuating the
unadjusted results. The magnitude of association for each of these variables was
fairly consistent for each beta-cell function measure. For every one SD increase
in any of these three NEFA variables, there was an average predicted
`r est_gee$est[1]`% lower IGI/IR and `r est_gee$est[2]`% lower ISSI-2 at each
clinic visit. However, in contrast to these results using NEFA modeled as
concentrations, none of the NEFA variables modeled as mol% were associated with
the outcomes. Adjusting for TAG attenuated all associations with IGI/IR and
ISSI-2 (data not shown), though this may be due to the fact that only a subset
of participants at the 6 year visit had TAG measured. Sensitivity analyses to
examine the association with
the sum of fatty acid classes (saturated vs unsaturated) revealed similar
findings as seen with the adjusted GEE model for total NEFA (data not shown).
There were no significant interaction effects between time, sex, or ethnicity
and the individual NEFA on any of the outcome measures.
Raw values from the GEE models are shown in `r cite_st('gee')` for
fully adjusted models and `r cite_st('gee_unadj')` for unadjusted models.
Consistent with the GEE modeling, results from modeling all NEFA in a
multivariate environment using PLS showed no discernible clustering nor was it
predictive of the outcomes (data not shown).

>>>>

A number of associations were seen in the unadjusted GEE models 
(see `r cite_f('gee_unadj')`), particularly for NEFA modeled as a concentration.
While full model adjustment (`r cite_f('gee_adj')`) attenuated most of these
associations, total NEFA, 16:0, 18:1n-9, and 18:2n-6 (all as nmol/mL)
continued to show negative associations with IGI/IR and ISSI-2. Sensitivity
analyses revealed that adjustment for WC was responsible for attenuating the
unadjusted results. The magnitude of association for each of these variables was
fairly consistent for each beta-cell function measure. For every one SD increase
in any of these three NEFA variables, there was an average predicted
`r est_gee$est[1]`% lower IGI/IR and `r est_gee$est[2]`% lower ISSI-2 at each
clinic visit. However, in contrast to these results using NEFA modeled as
concentrations, none of the NEFA variables modeled as mol% were associated with
the outcomes. Adjusting for TAG attenuated all associations with IGI/IR and
ISSI-2 (data not shown), though this may be due to the fact that only a subset
of participants at the 6 year visit had TAG measured. Sensitivity analyses to
examine the association with
the sum of fatty acid classes (saturated vs unsaturated) revealed similar
findings as seen with the adjusted GEE model for total NEFA (data not shown).
There were no significant interaction effects between time, sex, or ethnicity
and the individual NEFA on any of the outcome measures.
Raw values from the GEE models are shown in `r cite_st('gee_unadj')` for
unadjusted models and `r cite_st('gee_adj')` for fully adjusted models.
Consistent with the GEE modeling, results from modeling all NEFA in a
multivariate environment using PLS showed no discernible clustering nor was it
predictive of the outcomes (data not shown).
